---
title: "Psylocibin Plot"
author: "EFIT Program"
date: "15/8/2022"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: true
  toc_depth: 3
  number_sections: true
---

# Psylocibin Plots

In the following "chunk" you will find the code for importing the libraries, import and set the database, and to subset the original database for each one of the plots.

```{r message=FALSE, warning=FALSE}
# Libraries. 
library(tidyverse)
library(xlsx)
library(psych)
library(ggrepel)
library(viridis)
library(ggpubr)
library(cowplot)

# Importing the database. 
Data <- read.xlsx2("DataBaseOK.xlsx", sheetIndex = 1)

# Setting variables. 
{
  Data$Findings <- as.factor(Data$Findings)
  Data$Type_Dosage <- as.character(Data$Type_Dosage)
  Data$Dosage <- as.numeric(Data$Dosage)
  Data$Period <- as.factor(Data$Period)
  Data$Finding <- as.factor(Data$Finding)
  Data$Construct <- as.factor(Data$Construct)
  Data$Frequency <- as.numeric(Data$Frequency)
}

# Create the column for the size. 
# This column helps to adjust the size for all the points in the plots. 
Data$FreqSize <- Data$Frequency*2.5
```

# Background Colors.

For the plots background a set of two different colors were created.

## First Palette: For plots.

```{r message=FALSE, warning=FALSE}

# Creating the pallete for the background. 
BGcolor <- colorRampPalette(c("#FDE725","#31688E","#6ECE58"))
Backgrounds <- BGcolor(20)
plot(1:20, pch = 15, col = Backgrounds, cex=2.5)
```

## Second Palette: For Legend.

```{r message=FALSE, warning=FALSE}
# This is to create a second, alternative pallette, 
BGcolor2 <- colorRampPalette(c("#6ECE58","#31688E","#FDE725"))
Backgrounds2 <- BGcolor2(20)
plot(1:20, pch = 15, col = Backgrounds2, fill = Backgrounds2,
     cex = 3)

```

# Pos/Neg Rates.

## Data Subsets.

For all the plots the "Subjective" construct will be removed order to make them more understandable.

```{r}
# To Plot 1
toP1 <- subset(Data,Data$Period == "Acute" &
                Data$Type_Dosage == "Variable Dosage (ug/kg)")

# To Plot 2
toP2 <- subset(Data,Data$Period == "Post_acute" &
                Data$Type_Dosage == "Variable Dosage (ug/kg)")

# To Plot 3
toP3 <- subset(Data,Data$Period == "Acute" &
                Data$Type_Dosage == "Fixed Dosage (mg)")

# To Plot 4
toP4 <- subset(Data,Data$Period == "Post_acute" &
                Data$Type_Dosage == "Fixed Dosage (mg)")

```

## Rates Calculation.

```{r}
#To plot1 
# "Creating" the color for the Background.
# The rate of Positive to Negative findings is estimated for each plot. 

# Create the table to know the frequency for each Finding.
T1 <- table(toP1$Finding)
# Transform the table into a Dataframe. 
T1 <- as.data.frame(T1)
# Calculating the rate.
BgP1 <- (T1$Freq[1]-T1$Freq[3])/sum(T1$Freq[3],T1$Freq[1])*100
BgP1 <- round(BgP1)

#To plot2 
T2 <- table(toP2$Finding)
T2 <- as.data.frame(T2)
BgP2 <- (T2$Freq[1]-T2$Freq[3])/sum(T2$Freq[3],T2$Freq[1])*100
BgP2 <- round(abs(BgP2))

#To plot3 
T3 <- table(toP3$Finding)
T3 <- as.data.frame(T3)
BgP3 <- (T3$Freq[1]-T3$Freq[3])/sum(T3$Freq[3],T3$Freq[1])*100
BgP3 <- round(abs(BgP3))

#To plot4 
T4 <- table(toP4$Finding)
T4 <- as.data.frame(T4)
BgP4 <- (T4$Freq[1]-T4$Freq[3])/sum(T4$Freq[3],T4$Freq[1])*100
BgP4 <- round(abs(BgP4))

```

For each plot a Negative Vs. Positive rate was calculated. As follows:

$$
\frac{Negatives- Positives}{Positives+Negatives}*100
$$

To ease the color assignation for the backgrounds the results were rounded to the most proximate integer.

# Plot 0: Background Legend.

```{r}
#BGData <- c(BgP1, BgP2, BgP3, BgP4) 
BGData <- c(1:20)
BGData <- as.data.frame(BGData)
names(BGData) <- "PlotBG"
BGData$PlotBG <- as.numeric(BGData$PlotBG)

PA <- ggplot(BGData, aes(x=PlotBG,y=PlotBG))+
  geom_point(aes(colour = PlotBG),size = 5)+
  scale_colour_gradientn(colours= BGcolor(5),
                        limits = c(1,5),
                        labels = c("More\nNegative","More\nPositive"),
                        breaks = c(1,5))+
  theme(legend.position = "top",
        legend.title.align = 0.5,
        legend.text = element_text(size=8))+
  guides(colour = guide_colorbar(
    title = "Overall valence\n(Background colour)",
    title.theme = element_text(hjust = 0.5,
                               vjust = 0.5,
                               size = 9, 
                               face = "bold"),
    title.position = "top",
    title.hjust = 0.5,
    title.vjust = 1,
    barwidth = 6,
    barheight = 0.5))
  
PA
```

# Plot 1: General Legend.

This "plot" is coded because of the need of "one" legend for all the plots.

```{r eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
P0 <- ggplot(subset(Data, Data$Construct != "Subjective"),
             aes(x = Dosage, y = Frequency)) + 
  geom_point(aes(
    fill = FinalResult,
    shape = FinalResult,
    size = FreqSize),
    alpha=0.75, colour = "black", show.legend = T)+
  scale_fill_manual(values = c("#FDE725","#31688E","#6ECE58",
                               "#FDE725","#31688E",
                               "#31688E",
                               "#FDE725","#31688E","#6ECE58",
                               "#FDE725","#31688E","#6ECE58",
                               "#FDE725"))+
  scale_shape_manual(values = c(22,22,22,
                                21,21,
                                24,
                                25,25,25,
                                23,23,23,
                                14))+
  scale_x_continuous(expand=c(0,0),limits = c(0,450), breaks = seq(0,450,50))+
  scale_y_continuous(expand= c(0,0),limits = c(0,9.5), breaks = seq(0:9))+
  labs(fill = "Group",
       shape = "Group")+
  theme_light()+
  guides(size = "none")

P0

```

```{r}
P0_s <- ggplot(subset(Data, Data$Construct != "Subjective"),
             aes(x = Dosage, y = Frequency)) + 
  geom_point(aes(
    fill = Finding,
    color = Finding,
    shape = Construct),
    alpha=1, show.legend = T)+
  scale_fill_manual(values = c("#FDE725","#31688E","#6ECE58"))+
  scale_color_manual(values = c("#FDE725","#31688E","#6ECE58"))+
  scale_shape_manual(values = c(22,21,24,25,23,14))+
  labs(fill = "Valence\n(Colour)",
       colour = "Valence\n(Colour)",
       shape = "Construct\n(Shape)")+
  theme_light()+
  theme(
    legend.title = element_text(face = "bold", size=9),
    legend.key.size = unit(2, 'line'),
    legend.key.height = unit(1, 'line'),
    legend.key.width = unit(1.2, 'line'),
    legend.title.align = 0.5,
    legend.box.just = "center"
    )+
  guides(
    color = guide_legend(override.aes = list(size=5)),
    shape = guide_legend(override.aes = list(size=2.5,
                                             fill = "black")))
P0_s

```

# Plot 2: Acute - Variable Dosage.

As all the plots follows the same "steps", only Plot 1 will be completely commented.

```{r eval=FALSE, include=FALSE}
# Plot 1
# First, you need to create a "space" for the plot.
# Here the data is subsetting to fit the needs.
P1 <- ggplot(subset(Data,Data$Period == "Acute" &
                Data$Type_Dosage == "Variable Dosage (ug/kg)"& 
                  Data$Construct != "Subjective"), 
       aes(x = Dosage, y = Frequency)) + 
  # Then you add the "Points"
  geom_point(aes(
    # The fill color is decided by the FinalResult variable.
    fill = FinalResult,
    # As well as the shape for each point.
    shape = FinalResult,
    # The size is determined by the FreqSize variable.
    size = FreqSize),
    # The "transparency", and outline are setting here.
    alpha=0.75, colour = "black")+
  # Then, the color for each caegory is setted manually.
  # Note: For each plot the code is different.
  scale_fill_manual(values = c("#FDE725","#31688E","#6ECE58",
                               "#FDE725","#31688E",
                               "#FDE725","#31688E",
                               "#FDE725","#31688E","#6ECE58",
                               "#FDE725"))+
  # Same with the shapes. 
  scale_shape_manual(values = c(22,22,22,
                                21,21,
                                25,25,
                                23,23,23,
                                14))+
  # Set the limits and brackets for X-axis.
  scale_x_continuous(expand=c(0,0),limits = c(0,450), breaks = seq(0,450,50))+
  # Set the limits and brackets for Y-axis.
  scale_y_continuous(expand= c(0,0),limits = c(0,9.5), breaks = seq(0:9))+
  # Set the labels for the plot. 
  labs(title = "Acute Effects - Variable Dosage",
       x = "Psilocybin Dosage (ug/kg)",
       y = "Frequency of Effect",
       fill = "Group",
       shape = "Group")+
  # Add the "Theme"
  theme_light()+
  # Custom the "Theme". 
    theme(
      # Center the main title and set the size.
      plot.title = element_text(size = 9,hjust=0.5),
      # Set the size for the axis titles. 
      axis.title = element_text(size = 9),
      # Set the size for x-axis hints. 
      axis.text.x = element_text(size = 7),
      # Hide the grid for the background.
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      # Set the color and transparency for the background according to the +/- rate. 
      panel.background = element_rect(
        fill = adjustcolor(Backgrounds[BgP1],
                           alpha.f = 0.3)))+
  # Hide the size in the Legend. 
  guides(size = "none")


P1

```

```{r}
# Plot 1 "Simplified". 
P1_s <- ggplot(subset(Data,Data$Period == "Acute" &
                Data$Type_Dosage == "Variable Dosage (ug/kg)"& 
                  Data$Construct != "Subjective"), 
       aes(x = Dosage, y = Frequency)) + 
  geom_point(aes(
    fill = Finding,
    color = Finding,
    shape = Construct,
    size = FreqSize),
    alpha=1)+
  geom_point(aes(shape = Construct, size = FreqSize),
             colour = "black", show.legend = F)+
  scale_fill_manual(values = c("#FDE725","#31688E","#6ECE58"))+
  scale_color_manual(values = c("#FDE725","#31688E","#6ECE58"))+
  scale_shape_manual(values = c(22,21,25,23,14))+
  scale_x_continuous(expand=c(0,0),limits = c(0,450),
                     breaks = seq(0,450,50))+
  scale_y_continuous(expand= c(0,0),limits = c(0,9.5), 
                     breaks = seq(0:9))+
  labs(title = "Acute Effects - Variable Dosage",
       x = "Psilocybin Dosage (ug/kg)",
       y = "Frequency of Effect",
       fill = "Finding",
       colour = "Finding",
       shape = "Construct")+
  theme_light()+
    theme(
      plot.title = element_text(size = 9,hjust=0.5),
      axis.title = element_text(size = 9),
      axis.text.x = element_text(size = 7),
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      panel.background = element_rect(
      fill = adjustcolor(Backgrounds2[18],
                           alpha.f = 0.3)))+
  guides(size = "none")

P1_s

```

# Plot 3: Post Acute - Variable Dosage

```{r eval=FALSE, include=FALSE}
# Plot 2. 
P2 <- ggplot(subset(Data,Data$Period == "Post_acute" &
                Data$Type_Dosage == "Variable Dosage (ug/kg)"), 
       aes(x = Dosage, y = Frequency)) + 
  geom_point(aes(
    fill = FinalResult,
    shape = FinalResult,
    size = FreqSize),
    alpha=0.75, colour = "black", show.legend = T)+
  scale_fill_manual(values = c("#FDE725","#31688E","#6ECE58",
                               "#31688E","#6ECE58",
                               "#FDE725","#31688E"))+
  scale_shape_manual(values = c(22,22,22,
                                25,25,
                                23,23))+
  scale_x_continuous(expand=c(0,0),
                     limits = c(0,450), breaks = seq(0,450,50))+
  scale_y_continuous(expand= c(0,0),
                     limits = c(0,9.5), breaks = seq(0:9))+
  labs(title = "Post Acute Effects - Variable Dosage",
       x = "Psilocybin Dosage (ug/kg)",
       y = "Frequency of Effect",
       fill = "Group",
       shape = "Group")+
  theme_light()+
    theme(
      plot.title = element_text(size = 9,hjust=0.5),
      axis.title = element_text(size = 9),
      axis.text.x = element_text(size = 7),
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      panel.background = element_rect(
        fill = adjustcolor(Backgrounds[BgP2],
                           alpha.f = 0.3)))+
  guides(size = "none")

P2
```

```{r}
# Plot 2. 
P2_s <- ggplot(subset(Data,Data$Period == "Post_acute" &
                Data$Type_Dosage == "Variable Dosage (ug/kg)"), 
       aes(x = Dosage, y = Frequency)) + 
  geom_point(aes(
    fill = Finding,
    color = Finding,
    shape = Construct,
    size = FreqSize),
    alpha=1, show.legend = T)+
  geom_point(aes(shape = Construct, size = FreqSize),
             colour = "black", show.legend = F)+
  scale_fill_manual(values = c("#FDE725","#31688E","#6ECE58"))+
  scale_color_manual(values = c("#FDE725","#31688E","#6ECE58"))+
  scale_shape_manual(values = c(22,25,23))+
  scale_x_continuous(expand=c(0,0),
                     limits = c(0,450), breaks = seq(0,450,50))+
  scale_y_continuous(expand= c(0,0),
                     limits = c(0,9.5), breaks = seq(0:9))+
  labs(title = "Post Acute Effects - Variable Dosage",
       x = "Psilocybin Dosage (ug/kg)",
       y = "Frequency of Effect",
       fill = "Finding",
       colour = "Finding",
       shape = "Construct")+
  theme_light()+
    theme(
      plot.title = element_text(size = 9,hjust=0.5),
      axis.title = element_text(size = 9),
      axis.text.x = element_text(size = 7),
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      panel.background = element_rect(
        fill = adjustcolor(Backgrounds2[8],
                           alpha.f = 0.3)))+
  guides(size = "none")

P2_s

```

# Plot 4: Acute - Fixed Dosage

```{r eval=FALSE, include=FALSE}
# Plot 3. 
P3 <- ggplot(subset(Data,Data$Period == "Acute" &
                Data$Type_Dosage == "Fixed Dosage (mg)"), 
       aes(x = Dosage, y = Frequency)) + 
  geom_point(aes(
    fill = FinalResult,
    shape = FinalResult,
    size = FreqSize),
    alpha=0.75, colour = "black", show.legend = T)+
  scale_fill_manual(values = c("#31688E","#6ECE58","#31688E"))+
  scale_shape_manual(values = c(22,22,21))+
  scale_x_continuous(expand=c(0,0),
                     limits = c(0,2), breaks = seq(0,2,0.2))+
  scale_y_continuous(expand= c(0,0),
                     limits = c(0,9.5), breaks = seq(0:9))+
  labs(title = "Acute Effects - Fixed Dosage",
       x = "Psilocybin Dosage (mg)",
       y = "Frequency of Effect",
       fill = "Group",
       shape = "Group")+
  theme_light()+
    theme(
      plot.title = element_text(size = 9,hjust=0.5),
      axis.title = element_text(size = 9),
      axis.text.x = element_text(size = 7),
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      panel.background = element_rect(
        fill = adjustcolor(Backgrounds[BgP3],
                           alpha.f = 0.3)))+
  guides(size = "none")

P3

```

```{r}
# Plot 3. 
P3_s <- ggplot(subset(Data,Data$Period == "Acute" &
                Data$Type_Dosage == "Fixed Dosage (mg)"), 
       aes(x = Dosage, y = Frequency)) + 
  geom_point(aes(
    fill = Finding,
    color = Finding,
    shape = Construct,
    size = FreqSize),
    alpha=1, show.legend = T)+
    geom_point(aes(shape = Construct, size = FreqSize),
             colour = "black", show.legend = F)+
  scale_fill_manual(values = c("#31688E","#6ECE58"))+
  scale_color_manual(values = c("#31688E","#6ECE58"))+
  scale_shape_manual(values = c(22,22,21))+
  scale_x_continuous(expand=c(0,0),
                     limits = c(0,2), breaks = seq(0,2,0.2))+
  scale_y_continuous(expand= c(0,0),
                     limits = c(0,9.5), breaks = seq(0:9))+
  labs(title = "Acute Effects - Fixed Dosage",
       x = "Psilocybin Dosage (mg)",
       y = "Frequency of Effect",
       fill = "Finding",
       colour = "Finding",
       shape = "Construct")+
  theme_light()+
    theme(
      plot.title = element_text(size = 9,hjust=0.5),
      axis.title = element_text(size = 9),
      axis.text.x = element_text(size = 7),
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      panel.background = element_rect(
        fill = adjustcolor(Backgrounds2[1],
                           alpha.f = 0.3)))+
  guides(size = "none")

P3_s

```

# Plot 5: Post Acute - Fixed Dosage

```{r eval=FALSE, include=FALSE}
# Plot 4
P4 <- ggplot(subset(Data,Data$Period == "Post_acute" &
                Data$Type_Dosage == "Fixed Dosage (mg)"), 
       aes(x = Dosage, y = Frequency)) + 
  geom_point(aes(
    fill = FinalResult,
    shape = FinalResult,
    size = FreqSize),
    alpha=0.75, colour = "black", show.legend = T)+
  scale_fill_manual(values = c("#31688E","#31688E","#31688E","#6ECE58"))+
  scale_shape_manual(values = c(24,25,23,23))+
  scale_x_continuous(expand=c(0,0),
                     limits = c(0,50), breaks = seq(0,50,5))+
  scale_y_continuous(expand= c(0,0),
                     limits = c(0,9.5), breaks = seq(0:9))+
  labs(title = "Post Acute Effects - Fixed Dosage",
       x = "Psilocybin Dosage (mg)",
       y = "Frequency of Effect",
       fill = "Group",
       shape = "Group")+
  theme_light()+
    theme(
      plot.title = element_text(size = 9, hjust=0.5),
      axis.title = element_text(size = 9),
      axis.text.x = element_text(size = 7),
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      panel.background = element_rect(
        fill = adjustcolor(Backgrounds[BgP4],
                           alpha.f = 0.3)))+
  guides(size = "none")

P4

```

```{r}
# Plot 4
P4_s <- ggplot(subset(Data,Data$Period == "Post_acute" &
                Data$Type_Dosage == "Fixed Dosage (mg)"), 
       aes(x = Dosage, y = Frequency)) + 
  geom_point(aes(
    fill = Finding,
    color = Finding,
    shape = Construct,
    size = FreqSize),
    alpha=1, show.legend = T)+
    geom_point(aes(shape = Construct, size = FreqSize),
             colour = "black", show.legend = F)+
  scale_fill_manual(values = c("#31688E","#6ECE58"))+
  scale_color_manual(values = c("#31688E","#6ECE58"))+
  scale_shape_manual(values = c(24,25,23))+
  scale_x_continuous(expand=c(0,0),
                     limits = c(0,50), breaks = seq(0,50,5))+
  scale_y_continuous(expand= c(0,0),
                     limits = c(0,9.5), breaks = seq(0:9))+
  labs(title = "Post Acute Effects - Fixed Dosage",
       x = "Psilocybin Dosage (mg)",
       y = "Frequency of Effect",
       fill = "Finding",
       colour = "Finding",
       shape = "Construct")+
  theme_light()+
    theme(
      plot.title = element_text(size = 9, hjust=0.5),
      axis.title = element_text(size = 9),
      axis.text.x = element_text(size = 7),
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      panel.background = element_rect(
        fill = adjustcolor(Backgrounds2[1],
                           alpha.f = 0.3)))+
  guides(size = "none")

P4_s

```

# Final Plot.

```{r eval=FALSE, include=FALSE}
# Putting all plots together. 
allplots <- plot_grid(
  P1+theme(legend.position = "none"),
  P2+theme(legend.position = "none"),
  P3+theme(legend.position = "none"),
  P4+theme(legend.position = "none"),
  labels = c("(A)","(B)","(C)","(D)"),
  ncol = 2, nrow = 2, axis = "none",
  label_size = 9)

allplots

# Adding Shared Legend.
#Getting the legend from P0.
legend <- get_legend(P0 + theme(legend.box.margin = margin(0,0,0,0)))

# Merging the plots and the legend. 
plot_grid(allplots, legend, ncol = 2, nrow = 1,
          rel_widths = c(3, 1), scale =0.95)
```

```{r warning=FALSE}
# Putting all plots together. 
allplots_s <- plot_grid(
  P1_s+theme(legend.position = "none"),
  P2_s+theme(legend.position = "none"),
  P3_s+theme(legend.position = "none"),
  P4_s+theme(legend.position = "none"),
  labels = c("(A)","(B)","(C)","(D)"),
  ncol = 2, nrow = 2, axis = "none", label_size = 9)

allplots_s

# Adding the Legend.
#Getting the legend from PA
BGlegend <- get_legend(PA + theme(legend.box.margin = 
                                    margin(-100,0,0,0)))
#Getting the legend from P0.
legend <- get_legend(P0_s + theme(legend.box.margin = margin(-55,0,0,0)))

# Merging the plots and the legend. 
PlotA <- plot_grid(legend, BGlegend, ncol = 1, nrow = 2,
                   rel_heights = c(20, 1), scale =0.90)
PlotA

PlotB <- plot_grid(allplots_s, PlotA,ncol = 2, nrow = 1,
                   rel_widths = c(3, 1), scale =0.95)
PlotB
```

# Saving the Plot. 

```{r}
# Exporting the plot. 
ggsave("psylocibin.jpg", PlotB, 
       width = 180, units = "mm",
       dpi=300)

```
