---
title: "Psylocibin Plot"
author: "EFIT Program"
date: "15/8/2022"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: true
  toc_depth: 3
  number_sections: true
---

# Psylocibin Plots

In the following "chunk" you will find the code for importing the libraries, import and set the database, and to subset the original database for each one of the plots.

```{r message=FALSE, warning=FALSE}
# Libraries. 
library(tidyverse)
library(xlsx)
library(psych)
library(ggrepel)
library(viridis)
library(ggpubr)
library(cowplot)

# Importing the database. 
Data <- read.xlsx2("DataBaseOK.xlsx", sheetIndex = 1)

# Creating the pallete for the background. 
BGcolor <- colorRampPalette(c("#FDE725","#6ECE58"))
Backgrounds <- BGcolor(150)

# Setting variables. 
{
  Data$Findings <- as.factor(Data$Findings)
  Data$Type_Dosage <- as.character(Data$Type_Dosage)
  Data$Dosage <- as.numeric(Data$Dosage)
  Data$Period <- as.factor(Data$Period)
  Data$Finding <- as.factor(Data$Finding)
  Data$Construct <- as.factor(Data$Construct)
  Data$Frequency <- as.numeric(Data$Frequency)
}

# Create the column for the size. 
# This column helps to adjust the size for all the points in the plots. 
Data$FreqSize <- Data$Frequency*2.5



```

## Creating the subsets. 

For all the plot the "Subjective" construct will be removed order to make them more understandable.

```{r}
# To Plot 1
toP1 <- subset(Data,Data$Period == "Acute" &
                Data$Type_Dosage == "Variable Dosage (ug/kg)" & 
                 Data$Construct != "Subjective")

# To Plot 2
toP2 <- subset(Data,Data$Period == "Post_acute" &
                Data$Type_Dosage == "Variable Dosage (ug/kg)" & 
                 Data$Construct != "Subjective")

# To Plot 3
toP3 <- subset(Data,Data$Period == "Acute" &
                Data$Type_Dosage == "Fixed Dosage (mg)" & 
                 Data$Construct != "Subjective")

# To Plot 4
toP4 <- subset(Data,Data$Period == "Post_acute" &
                Data$Type_Dosage == "Fixed Dosage (mg)" & 
                 Data$Construct != "Subjective")

```

# Plot 0 - For Legend only.

This "plot" is coded because of the need of "one" legend for all the plots.

```{r message=FALSE, warning=FALSE}
P0 <- ggplot(subset(Data, Data$Construct != "Subjective"),
             aes(x = Dosage, y = Frequency)) + 
  geom_point(aes(
    fill = FinalResult,
    shape = FinalResult,
    size = FreqSize),
    alpha=0.75, colour = "black", show.legend = T)+
  scale_fill_manual(values = c("#FDE725","#31688E","#6ECE58",
                               "#FDE725","#31688E",
                               "#31688E",
                               "#FDE725","#31688E","#6ECE58",
                               "#FDE725","#31688E","#6ECE58",
                               "#FDE725"))+
  scale_shape_manual(values = c(22,22,22,
                                21,21,
                                24,
                                25,25,25,
                                23,23,23,
                                14))+
  scale_x_continuous(expand=c(0,0),limits = c(0,450), breaks = seq(0,450,50))+
  scale_y_continuous(expand= c(0,0),limits = c(0,9.5), breaks = seq(0:9))+
  labs(fill = "Group",
       shape = "Group")+
  theme_light()+
  guides(size = "none")

P0

```

# Plot 1: Acute - Variable Dosage.

As all the plots follows the same "steps", only Plot 1 will be completely commented.

```{r}
# "Creating" the color for the Background.
# The rate of Positive to Negative findings is estimated for each plot. 

# Create the table to know the frequency for each Finding.
T1 <- table(toP1$Finding)
# Transform the table into a Dataframe. 
T1 <- as.data.frame(T1)
# Calculating the rate.
BgP1 <- (T1$Freq[3]/T1$Freq[1])*100

# Plot 1
# First, you need to create a "space" for the plot.
# Here the data is subsetting to fit the needs.
P1 <- ggplot(subset(Data,Data$Period == "Acute" &
                Data$Type_Dosage == "Variable Dosage (ug/kg)"& 
                  Data$Construct != "Subjective"), 
       aes(x = Dosage, y = Frequency)) + 
  # Then you add the "Points"
  geom_point(aes(
    # The fill color is decided by the FinalResult variable.
    fill = FinalResult,
    # As well as the shape for each point.
    shape = FinalResult,
    # The size is determined by the FreqSize variable.
    size = FreqSize),
    # The "transparency", and outline are setting here.
    alpha=0.75, colour = "black")+
  # Then, the color for each caegory is setted manually.
  # Note: For each plot the code is different.
  scale_fill_manual(values = c("#FDE725","#31688E","#6ECE58",
                               "#FDE725","#31688E",
                               "#FDE725","#31688E",
                               "#FDE725","#31688E","#6ECE58",
                               "#FDE725"))+
  # Same with the shapes. 
  scale_shape_manual(values = c(22,22,22,
                                21,21,
                                25,25,
                                23,23,23,
                                14))+
  # Set the limits and brackets for X-axis.
  scale_x_continuous(expand=c(0,0),limits = c(0,450), breaks = seq(0,450,50))+
  # Set the limits and brackets for Y-axis.
  scale_y_continuous(expand= c(0,0),limits = c(0,9.5), breaks = seq(0:9))+
  # Set the labels for the plot. 
  labs(title = "Acute Effects - Variable Dosage",
       x = "Psilocybin Dosage (ug/kg)",
       y = "Frequency of Effect",
       fill = "Group",
       shape = "Group")+
  # Add the "Theme"
  theme_light()+
  # Custom the "Theme". 
    theme(
      # Center the main title and set the size.
      plot.title = element_text(size = 11,hjust=0.5),
      # Set the size for the axis titles. 
      axis.title = element_text(size = 9),
      # Hide the grid for the background.
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      # Set the color and transparency for the background according to the +/- rate. 
      panel.background = element_rect(
        fill = adjustcolor(Backgrounds[BgP1],
                           alpha.f = 0.3)))+
  # Hide the size in the Legend. 
  guides(size = "none")


P1

```

# Plot 2: Post Acute - Variable Dosage

```{r}
# "Creating" the color for the Background. 
T2 <- table(toP2$Finding)
T2 <- as.data.frame(T2)
BgP2 <- (T2$Freq[3]/T2$Freq[1])*100

# Plot 2. 
P2 <- ggplot(subset(Data,Data$Period == "Post_acute" &
                Data$Type_Dosage == "Variable Dosage (ug/kg)"), 
       aes(x = Dosage, y = Frequency, fill = Findings)) + 
  geom_point(aes(
    fill = FinalResult,
    shape = FinalResult,
    size = FreqSize),
    alpha=0.75, colour = "black", show.legend = T)+
  scale_fill_manual(values = c("#FDE725","#31688E","#6ECE58",
                               "#31688E","#6ECE58",
                               "#FDE725","#31688E"))+
  scale_shape_manual(values = c(22,22,22,
                                25,25,
                                23,23))+
  scale_x_continuous(expand=c(0,0),
                     limits = c(0,450), breaks = seq(0,450,50))+
  scale_y_continuous(expand= c(0,0),
                     limits = c(0,9.5), breaks = seq(0:9))+
  labs(title = "Post-Acute Effects - Variable Dosage",
       x = "Psilocybin Dosage (ug/kg)",
       y = "Frequency of Effect",
       fill = "Group",
       shape = "Group")+
  theme_light()+
    theme(
      plot.title = element_text(size = 11,hjust=0.5),
      axis.title = element_text(size = 9),
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      panel.background = element_rect(
        fill = adjustcolor(Backgrounds[BgP2],
                           alpha.f = 0.3)))+
  guides(size = "none")

P2
```

# Plot 3: Acute - Fixed Dosage

```{r}
# "Creating" the color for the Background. 
T3 <- table(toP3$Finding)
T3 <- as.data.frame(T3)
BgP3 <- T3$Freq[3]*50

# Plot 3. 
P3 <- ggplot(subset(Data,Data$Period == "Acute" &
                Data$Type_Dosage == "Fixed Dosage (mg)"), 
       aes(x = Dosage, y = Frequency, fill = Findings)) + 
  geom_point(aes(
    fill = FinalResult,
    shape = FinalResult,
    size = FreqSize),
    alpha=0.75, colour = "black", show.legend = T)+
  scale_fill_manual(values = c("#31688E","#6ECE58","#31688E"))+
  scale_shape_manual(values = c(22,22,21))+
  scale_x_continuous(expand=c(0,0),
                     limits = c(0,2), breaks = seq(0,2,0.2))+
  scale_y_continuous(expand= c(0,0),
                     limits = c(0,9.5), breaks = seq(0:9))+
  labs(title = "Acute Effects - Fixed Dosage",
       x = "Psilocybin Dosage (ug/kg)",
       y = "Frequency of Effect",
       fill = "Group",
       shape = "Group")+
  theme_light()+
    theme(
      plot.title = element_text(size = 11,hjust=0.5),
      axis.title = element_text(size = 9),
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      panel.background = element_rect(
        fill = adjustcolor(Backgrounds[BgP3],
                           alpha.f = 0.3)))+
  guides(size = "none")

P3

```

# Plot 4: Post Acute - Fixed Dosage

```{r}
# "Creating" the color for the Background. 
T4 <- table(toP4$Finding)
T4 <- as.data.frame(T4)
BgP4 <- T4$Freq[3]*50

# Plot 4
P4 <- ggplot(subset(Data,Data$Period == "Post_acute" &
                Data$Type_Dosage == "Fixed Dosage (mg)"), 
       aes(x = Dosage, y = Frequency, fill = Findings)) + 
  geom_point(aes(
    fill = FinalResult,
    shape = FinalResult,
    size = FreqSize),
    alpha=0.75, colour = "black", show.legend = T)+
  scale_fill_manual(values = c("#31688E","#31688E","#31688E","#6ECE58"))+
  scale_shape_manual(values = c(24,25,23,23))+
  scale_x_continuous(expand=c(0,0),
                     limits = c(0,50), breaks = seq(0,50,5))+
  scale_y_continuous(expand= c(0,0),
                     limits = c(0,9.5), breaks = seq(0:9))+
  labs(title = "Post Acute Effects - Fixed Dosage",
       x = "Psilocybin Dosage (ug/kg)",
       y = "Frequency of Effect",
       fill = "Group",
       shape = "Group")+
  theme_light()+
    theme(
      plot.title = element_text(size = 11, hjust=0.5),
      axis.title = element_text(size = 9),
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      panel.background = element_rect(
        fill = adjustcolor(Backgrounds[BgP4],
                           alpha.f = 0.3)))+
  guides(size = "none")

P4

```

# Putting all together.

```{r}
# Putting all plots together. 
allplots <- plot_grid(
  P1+theme(legend.position = "none"),
  P2+theme(legend.position = "none"),
  P3+theme(legend.position = "none"),
  P4+theme(legend.position = "none"),
  labels = c("A","B","C","D"),
  ncol = 2, nrow = 2, axis = "none",
  label_size = 9)

allplots

# Adding Shared Legend.
#Getting the legend from P0.
legend <- get_legend(P0 + theme(legend.box.margin = margin(0,0,0,0)))

# Merging the plots and the legend. 
plot_grid(allplots, legend, ncol =2, nrow = 1,
          rel_widths = c(2.7, 1))
```
